---
title: "Shapley"
author: "Fabio Incerti"
date: "`r Sys.Date()`"
output: html_document
---

Clean the environment
```{r}
rm(list=ls()) 
```

```{r warning = FALSE}
library(dbarts)
library(haven)
library(fastshap)
library(ranger)
library(ggplot2)
library(imputeMissings)
library(patchwork)
library(tictoc)
library(xgboost)
source('C:/Users/fabio/OneDrive/Documenti/GitHub/machine-learning-for-zombie-hunting/R_code/REVIEW_year_by_year_analyses/functions.R')
```

Set Working Directory
```{r}
setwd("C:/Users/fabio/OneDrive/Documenti/GitHub/machine-learning-for-zombie-hunting/R_code/REVIEW_Shapley")
```

```{r}
pred_fun <- function(model, newdata, y) {
      #predict(model, newdata)$predictions[,2]
      pred = predict(model, newdata, mu = mean(y))
    }
```



Upload data
```{r}
data <- read_dta("H://.shortcut-targets-by-id//1keYb51HXkcQwzkU2kBgbnguQaqUy3umX//Zombie Hunting New Data/analysis_data_indicators.dta")
```


Get italian data
```{r}
data <- data[which(data$iso=="IT"),] 
names(data)[names(data) == 'GUO___BvD_ID_number'] <- 'guo'

data$control <- ifelse(data$guo=="", 0, 1)
data$nace <- as.factor(data$nace)
data$area <- as.factor(data$area)

levels(data$nace) <- floor(as.numeric(levels(data$nace))/100) 
```

Rename incorrectly labeled variables:
- misallocated_2008_fixed -> misallocated_fixed_2008
- revenue2008 -> revenue_2008
- depr2008 -> depr_2008
```{r}
for (i in c(2008:2016)) {
  colnames(data) <- gsub(paste("misallocated", sep="_", i, "fixed"), paste("misallocated", sep="_", "fixed", i), colnames(data))
  colnames(data) <- gsub(paste("revenue", sep="", i), paste("revenue", sep="_", i), colnames(data))
  colnames(data) <- gsub(paste("depr", sep="", i), paste("depr", sep="_", i), colnames(data))
}
```


Construct yearly failure Indicator
```{r}
data <- failure_yearly(data)
```


Define predictors
```{r}
# Time-variant predictors
lagged_predictors <- c("shareholders_funds",
                       "added_value", "cash_flow", "ebitda",
                       "fin_rev", "liquidity_ratio", "total_assets",
                       "depr", "long_term_debt", "employees",
                       "materials", "loans", "wage_bill", "tfp_acf",
                       "fixed_assets", "tax", "current_liabilities",
                       "current_assets", "fin_expenses", "int_paid",
                       "solvency_ratio", "net_income", "revenue",
                       "capital_intensity", "fin_cons", "inv",
                       "ICR_failure", "interest_diff", "NEG_VA",
                       "real_SA", "profitability", "misallocated_fixed",
                       "financial_sustainability", "liquidity_return",
                       "int_fixed_assets")

# Time-invariant predictors
predictors <- c("control", "nace", "consdummy", "area", "dummy_patents", "dummy_trademark")
```


Compute SHAP values
```{r}
years <- c(2010:2017)
shapley <- c()

tic()
  for (i in (years)){
    
    # Subset data by Year
    data_model <- data[which(!is.na(data[,paste("failure", sep = "_", i)])),]
    
    # Get Outcome Vector
    y <- as.vector(data_model[,paste("failure", sep = "_", i)])
    # y <- as.factor(unlist(y, use.names = FALSE))
    
    
    # Get Predictors Matrix
    data_model <- as.data.frame(cbind(y, data_model[,paste(lagged_predictors, sep = "_", i - 1)], data_model[, paste(predictors)]))
    
    # Generate NA Variable: count the number of NA for each row
    MissCount = rowSums(is.na(data_model))
    
    # Mark observations based on the number of NA: 35 is the cardinality of "lagged_predictors"
    miss = rep(NA, nrow(data_model))
    miss[which(MissCount == 0)] = 0                      # No time-variant predictor is missing
    miss[which(MissCount > 0 & MissCount < 35)] = 1      # Some time-variant predictors is missing
    miss[which(MissCount == 35)] = 2                     # All time-variant predictors at (i-1) are missing

    y <- data_model[, 1]
    X <- data_model[, -1]
    X <- impute(X, object = NULL, method = "median/mode", flag = FALSE)
    X <- cbind(X, miss)
    temp <- colnames(X)
    
    # XGBoost requires matrix format for the predictor matrix
    X <- matrix(unlist(X), ncol = length(X), nrow = nrow(X))
    colnames(X) <- temp
    
    # Run the model
    set.seed(42)
    xgboost <- xgboost(data = X, 
                       label = y, 
                       objective = "binary:logistic", 
                       nrounds = 100)

    
    # Compute fast (approximate) Shapley values for the set of features
    shap <- explain(xgboost, X = X, pred_wrapper = predict, nsim = 1, newdata = X)
    colnames(shap) <- c(lagged_predictors, predictors, paste("miss"))
    shapley <- rbind(shapley, shap)
  }
toc()
  
write.csv(shapley,"shapley.csv", row.names = FALSE)
```


(Figure 6) Compute the mean Shapley values and plot them
```{r}
# Sum up the values computed for each observation and divide by the number of observations
shap_imp <- data.frame(Variable = names(shapley),
                       Importance = apply(shapley, MARGIN = 2, FUN = function(x) sum(abs(x))/nrow(shapley) )
)

# Define new labels for ggplot
new.names <-  c(control = "Corporate control",
                miss = "Missingness",
                net_income = "Net income",
                employees = "Employees",
                tax = "Tax",
                real_SA = "Size-Age",
                fixed_assets = "Fixed assets",
                shareholders_funds = "Shareholders funds",
                revenue = "Revenues",
                tfp_acf = "TFP",
                inv = "Investement indicator",
                current_liabilities = "Current liabilities",
                current_assets = "Current assets",
                wage_bill = "Cost of employees",
                solvency_ratio = "Solvency ratio",
                total_assets = "Total assets",
                int_fixed_assets = "Intangible fixed assets",
                fin_rev = "Financial revenues",
                nace = "NACE rev. 2",
                materials = "Material costs",
                liquidity_return = "Liquidity return",
                fin_expenses = "Financial expenses",
                depr = "Depreciation",
                area = "Area",
                liquidity_ratio = "Liquidity ratio",
                ebitda = "EBITDA",
                int_paid = "Interest payments",
                financial_sustainability = "Financial sustainability",
                capital_intensity = "Capital intensity",
                loans = "Loans",
                added_value = "Added value",
                long_term_debt = "Long-term debt",
                cash_flow = "Cash flow",
                fin_cons = "Financial Constraints",
                interest_diff = "Benchmark interest difference",
                dummy_trademark = "Dummy trademarks",
                dummy_patents = "Dummy patents",
                misallocated_fixed = "Financial misallocation",
                ICR_failure = "ICR",
                profitability = "Profitability",
                consdummy = "Dummy consolidated accounts",
                NEG_VA = "Negative value added")


# Plot Shap-based variable importance
ggplot(shap_imp, aes(reorder(Variable, Importance), Importance)) +
       geom_col() +
       coord_flip() +
       scale_x_discrete(labels = new.names) +
       xlab("") +
       ylab("Shapley value") +
       theme(text = element_text(size=8) )
```






# NON-OVERLAP of variables among categories: each variable belongs to at most one group (partitioning the features space into groups)

(Figure 7) Compute the mean Shapley values for groups of variables
```{r}
sector <- c("nace")
shap_imp_sector <- data.frame(
  Variable = names(shapley[paste(sector)]),
  Importance = apply(shapley[paste(sector)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_sector <- sum(shap_imp_sector$Importance)

area <- c("area")
shap_imp_area <- data.frame(
  Variable = names(shapley[paste(area)]),
  Importance = apply(shapley[paste(area)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_area <- sum(shap_imp_area$Importance)

missingness <- c("miss")
shap_imp_miss <- data.frame(
  Variable = names(shapley[paste(missingness)]),
  Importance = apply(shapley[paste(missingness)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_miss <- sum(shap_imp_miss$Importance)

productivity <- c("tfp_acf")
shap_imp_productivity <- data.frame(
  Variable = names(shapley[paste(productivity)]),
  Importance = apply(shapley[paste(productivity)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_productivity <- sum(shap_imp_productivity$Importance)

size <- c("total_assets", "employees", "net_income")
shap_imp_size <- data.frame(
  Variable = names(shapley[,paste(size)]),
  Importance = apply(shapley[,paste(size)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_size <- sum(shap_imp_size$Importance)

profitability <- c("ebitda", "profitability")
shap_imp_profitability <- data.frame(
  Variable = names(shapley[,paste(profitability)]),
  Importance = apply(shapley[,paste(profitability)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_profitability <- sum(shap_imp_profitability$Importance)

governance <- c("control", "consdummy")
shap_imp_governance <- data.frame(
  Variable = names(shapley[,paste(governance)]),
  Importance = apply(shapley[,paste(governance)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_governance <- sum(shap_imp_governance$Importance)

innovation <- c("dummy_patents", "dummy_trademark")
shap_imp_innovation <- data.frame(
  Variable = names(shapley[,paste(innovation)]),
  Importance = apply(shapley[,paste(innovation)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_innovation <- sum(shap_imp_innovation$Importance)

financial_constraints <- c("real_SA", "financial_sustainability",
                           "liquidity_return", "int_fixed_assets", "fin_cons")

shap_imp_fin_cons <- data.frame(
  Variable = names(shapley[,paste(financial_constraints)]),
  Importance = apply(shapley[,paste(financial_constraints)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_fin_cons <- sum(shap_imp_fin_cons$Importance)

zombie_indicators <- c("ICR_failure", "NEG_VA", "interest_diff", "profitability",
                       "misallocated_fixed")
shap_imp_zombie <- data.frame(
  Variable = names(shapley[,paste(zombie_indicators)]),
  Importance = apply(shapley[,paste(zombie_indicators)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_zombie <- sum(shap_imp_zombie$Importance)

financial_accounts <- c("shareholders_funds", "added_value", "cash_flow", "inv",
                        "fin_rev", "liquidity_ratio", "depr", "long_term_debt", 
                        "materials", "loans", "wage_bill",  "fixed_assets", "tax",
                        "current_liabilities", "current_assets", "fin_expenses",
                        "int_paid","solvency_ratio", "revenue","capital_intensity")
shap_imp_fin_acc <- data.frame(
  Variable = names(shapley[,paste(financial_accounts)]),
  Importance = apply(shapley[,paste(financial_accounts)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_fin_acc <- sum(shap_imp_fin_acc$Importance)

# Group the Indicators
shap_imp_by_group <- data.frame(
  Variable = c("sector", "area", "size", "missingness", "profitability", "governance", "innovation",
               "productivity", "financial_constrains", "zombie_indicators", "financial_accounts"),
  Importance = c(shap_imp_sector, shap_imp_area, shap_imp_size, shap_imp_miss, shap_imp_profitability,
                 shap_imp_governance, shap_imp_innovation, shap_imp_productivity,
                 shap_imp_fin_cons, shap_imp_zombie, shap_imp_fin_acc)
)

shap_imp_by_group$Importance = shap_imp_by_group$Importance / nrow(shapley)

# Define new labels for ggplot
new.labels <-  c(financial_accounts = "Financial accounts",
                governance = "Governance",
                financial_constrains = "Financial constraints",
                size = "Size",
                missingness = "Missingness",
                productivity = "Productivity",
                sector = "Sector",
                area = "Area",
                profitability = "Profitability",
                zombie_indicators = "Zombie indicators",
                inv = "Investement indicator",
                innovation = "Innovation")

# Plot Shap-based variable importance
ggplot(shap_imp_by_group, aes(reorder(Variable, Importance), Importance)) +
        geom_col() +
        coord_flip() +
        xlab("") +
        scale_x_discrete(labels = new.labels) +
        ylab("Shapley value")  
```


# OVERLAP of variables among categories: each variable can belongs to more groups (additional analysis)

Compute the mean Shapley values for groups of variables
```{r}
# Aggregated Predictors (OVERLAP)
sector <- c("nace")
shap_imp_sector <- data.frame(
  Variable = names(shapley[paste(sector)]),
  Importance = apply(shapley[paste(sector)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_sector <- sum(shap_imp_sector$Importance)

area <- c("area")
shap_imp_area <- data.frame(
  Variable = names(shapley[paste(area)]),
  Importance = apply(shapley[paste(area)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_area <- sum(shap_imp_area$Importance)

missingness <- c("miss")
shap_imp_miss <- data.frame(
  Variable = names(shapley[paste(missingness)]),
  Importance = apply(shapley[paste(missingness)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_miss <- sum(shap_imp_miss$Importance)

size <- c("total_assets", "employees", "net_income")
shap_imp_size <- data.frame(
  Variable = names(shapley[,paste(size)]),
  Importance = apply(shapley[,paste(size)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_size <- sum(shap_imp_size$Importance)

profitability <- c("ebitda", "profitability")
shap_imp_profitability <- data.frame(
  Variable = names(shapley[,paste(profitability)]),
  Importance = apply(shapley[,paste(profitability)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_profitability <- sum(shap_imp_profitability$Importance)

governance <- c("control", "consdummy")
shap_imp_governance <- data.frame(
  Variable = names(shapley[,paste(governance)]),
  Importance = apply(shapley[,paste(governance)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_governance <- sum(shap_imp_governance$Importance)

innovation <- c("dummy_patents", "dummy_trademark")
shap_imp_innovation <- data.frame(
  Variable = names(shapley[,paste(innovation)]),
  Importance = apply(shapley[,paste(innovation)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_innovation <- sum(shap_imp_innovation$Importance)

productivity <- c("tfp_acf", "NEG_VA")
shap_imp_productivity <- data.frame(
  Variable = names(shapley[,paste(productivity)]),
  Importance = apply(shapley[,paste(productivity)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_productivity <- sum(shap_imp_productivity$Importance)

financial_constraints <- c("ICR_failure", "interest_diff", "NEG_VA", "real_SA", 
                           "misallocated_fixed", "financial_sustainability",
                           "liquidity_return", "int_fixed_assets", "fin_cons")
shap_imp_fin_cons <- data.frame(
  Variable = names(shapley[,paste(financial_constraints)]),
  Importance = apply(shapley[,paste(financial_constraints)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_fin_cons <- sum(shap_imp_fin_cons$Importance)

zombie_indicators <- c("ICR_failure", "NEG_VA", "interest_diff", "profitability",
                       "misallocated_fixed")
shap_imp_zombie <- data.frame(
  Variable = names(shapley[,paste(zombie_indicators)]),
  Importance = apply(shapley[,paste(zombie_indicators)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_zombie <- sum(shap_imp_zombie$Importance)

financial_accounts <- c("shareholders_funds", "added_value", "cash_flow", "inv",
                       "fin_rev", "liquidity_ratio", "depr", "long_term_debt", 
                       "materials", "loans", "wage_bill",  "fixed_assets", "tax",
                       "current_liabilities", "current_assets", "fin_expenses",
                       "int_paid","solvency_ratio", "revenue","capital_intensity")
shap_imp_fin_acc <- data.frame(
  Variable = names(shapley[,paste(financial_accounts)]),
  Importance = apply(shapley[,paste(financial_accounts)], MARGIN = 2, FUN = function(x) sum(abs(x)))
)
shap_imp_fin_acc <- sum(shap_imp_fin_acc$Importance)

# Group the Indicators
shap_imp_by_group <- data.frame(
  Variable = c("sector", "area", "size", "missingness", "profitability", "governance", "innovation",
               "productivity", "financial_constrains", "zombie_indicators", "financial_accounts"),
  Importance = c(shap_imp_sector, shap_imp_area, shap_imp_size, shap_imp_miss, shap_imp_profitability,
                 shap_imp_governance, shap_imp_innovation, shap_imp_productivity,
                 shap_imp_fin_cons, shap_imp_zombie, shap_imp_fin_acc)
)

shap_imp_by_group$Importance = shap_imp_by_group$Importance / nrow(shapley)


# Define new labels for ggplot
new.labels <-  c(financial_accounts = "Financial accounts",
                governance = "Governance",
                financial_constrains = "Financial constraints",
                size = "Size",
                missingness = "Missingness",
                producitivity = "Productivity",
                sector = "Sector",
                area = "Area",
                profitability = "Profitability",
                zombie_indicators = "Zombie indicators",
                inv = "Investement indicator",
                innovation = "Innovation")

# Plot Shap-based variable importance
ggplot(shap_imp_by_group, aes(reorder(Variable, Importance), Importance)) +
  geom_col() +
  coord_flip() +
  xlab("") +
  scale_x_discrete(labels = new.labels) +
  ylab("Shapley value")
```


